Fractional Types

### 2019-11-21 fracGC/p.tex
fix wrapfig
fix language about parity example

\begin{wrapfigure}{r}{0.2\textwidth}
  \input{parity.tikz}
\end{wrapfigure}  
\PIFDparity{}

\noindent The circuit exploits the additional expressiveness of
choosing the initial value of the ancilla (and sets it to true). When
applied to quantum inputs, the circuit detects whether the two qubits
are entangled in the state
$\frac{1}{\sqrt{2}}(\ket{00}+\ket{11})$. This property can be
confirmed from the classical behavior: if the inputs are anything
else, the ancilla bit is not restored to its original value (true) and
the dynamic check fails.

>>>>

\begin{wrapfigure}[0]{r}{0.2\textwidth}
  \input{parity.tikz}
\end{wrapfigure}  
\PIFDparity{}

\noindent The circuit initializes the ancilla to \textsf{true} and
checks that it remains \textsf{true} after interacting with the two
inputs. If either one of the inputs is \textsf{true} (but not both)
the ancilla bit will be negated and the runtime check would fail. Thus
the circuit can be used as a runtime assertion that the two inputs are
equal. When applied to quantum inputs, the circuit detects whether the
two qubits are entangled or not. By varying the initial value of the
ancilla, it is possible to customize the dynamic assertion to check
for particular entangled states~\cite{DBLP:journals/cal/ZhouB19}.
